Use of the package \texttt{fitdistrplus} to specify a distribution from non-censored or censored data

### 2011-04-07 inst/doc/intro2fitdistrplus.Rnw
correction of fitdistrplus vignette following Brian Ripley advice

The argument optim.method may be used in the call to \texttt{fitdist} or
\texttt{fitdistcens}. It will internally be passed to \texttt{mledist} and to \texttt{optim}.
This argument may be fixed to \texttt{"Nelder-Mead"} (the robust Nelder and Mead method), 
\texttt{"BFGS"} (the BFGS quasi-Newton method), \texttt{"CG"} (a conjugate gradients method), 
\texttt{"SANN"} (a variant of simulated annealing) or \texttt{"L-BFGS-B"} (a modification of the BFGS 
quasi-Newton method which enables box constraints optimization). For the use of the last method the 
arguments \texttt{lower} and/or \texttt{upper} also have to be passed. More details on these optimization
functions may be found in the help page of \texttt{optim} from the package \texttt{stats}.

@@

\section{Alternative methods to maximum likelihhod for non censored data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
For non censored data, alternative methods to maximum likelihood are available.

\subsection{Moment matching estimation}
%%%%%%%%%%
Moment matching may be performed fixing the argument \texttt{method}
to \texttt{"mme"} in the call to fitdist (see the help file page of the function
\texttt{mmedist} in \texttt{fitdistrplus} reference manual for details).
Below is an example of fit of a uniform distribution to data randomly
generated in a uniform distribution.
<<>>=
u <- runif(50,min=5,max=10)
fitdist(u,"unif",method="mme")
@

\subsection{Quantile matching estimation}
%%%%%%%%%%
Quantile matching may also be performed fixing the argument \texttt{method}
to \texttt{"qme"} in the call to fitdist and adding an argument \texttt{probs}
defining the probabilities for which the quantile matching is done.
The length of this vector must be equal
to the number of parameters to estimate.(see the help file page of the function
\texttt{qmedist} in \texttt{fitdistrplus} reference manual for details).
Below is an example of fit of a uniform distribution to the same dataset by matching first
and third quartiles.
<<>>=
fitdist(u,"unif",method="qme",probs=c(0.25,0.75))
@

\subsection{Maximum goodness-of-fit estimation}
%%%%%%%%%%
Parameters may also be estimated by maximizing a goodness-of-fit distance
by fixing the argument \texttt{method}
to \texttt{"mge"} in the call to fitdist and adding an argument \texttt{gof}
coding for the goodness-of-fit distance chosen. One may use the classical 
Cramer-von Mises distance (\texttt{"CvM"}), the classical
Kolmogorov-Smirnov distance (\texttt{"KS"}), the classical Anderson-Darling distance (\texttt{"AD"})
which gives more weight to the tails of the distribution,
or one of the variants of this last distance (see the help file page of the function
\texttt{mgedist} in \texttt{fitdistrplus} reference manual for details).
Below is an example of fit of a uniform distribution to the same dataset by maximizing the 
Kolmogorov-Smirnov distance.
<<>>=
fitdist(u,"unif",method="mge",gof="KS")
@

>>>>

The argument optim.method may be used in the call to \texttt{fitdist} or
\texttt{fitdistcens}. It will internally be passed to \texttt{mledist} and to \texttt{optim}.
This argument may be fixed to ``Nelder-Mead'' (the robust Nelder and Mead method), 
``BFGS'' (the BFGS quasi-Newton method), ``CG'' (a conjugate gradients method), 
``SANN'' (a variant of simulated annealing) or ``L-BFGS-B'' (a modification of the BFGS 
quasi-Newton method which enables box constraints optimization). For the use of the last method the 
arguments \texttt{lower} and/or \texttt{upper} also have to be passed. More details on these optimization
functions may be found in the help page of \texttt{optim} from the package \texttt{stats}.

@@

\section{Alternative methods to maximum likelihood for non censored data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
For non censored data, alternative methods to maximum likelihood are available.

\subsection{Moment matching estimation}
%%%%%%%%%%
Moment matching may be performed fixing the argument \texttt{method}
to ``mme'' in the call to fitdist (see the help file page of the function
\texttt{mmedist} in \texttt{fitdistrplus} reference manual for details).
Below is an example of fit of a uniform distribution to data randomly
generated in a uniform distribution.
<<>>=
u <- runif(50,min=5,max=10)
fitdist(u,"unif",method="mme")
@

\subsection{Quantile matching estimation}
%%%%%%%%%%
Quantile matching may also be performed fixing the argument \texttt{method}
to ``qme'' in the call to fitdist and adding an argument \texttt{probs}
defining the probabilities for which the quantile matching is done.
The length of this vector must be equal
to the number of parameters to estimate.(see the help file page of the function
\texttt{qmedist} in \texttt{fitdistrplus} reference manual for details).
Below is an example of fit of a uniform distribution to the same dataset by matching first
and third quartiles.
<<>>=
fitdist(u,"unif",method="qme",probs=c(0.25,0.75))
@

\subsection{Maximum goodness-of-fit estimation}
%%%%%%%%%%
Parameters may also be estimated by maximizing a goodness-of-fit distance
by fixing the argument \texttt{method}
to ``mge'' in the call to fitdist and adding an argument \texttt{gof}
coding for the goodness-of-fit distance chosen. One may use the classical 
Cramer-von Mises distance (``CvM''), the classical
Kolmogorov-Smirnov distance (``KS''), the classical Anderson-Darling distance (``AD'')
which gives more weight to the tails of the distribution,
or one of the variants of this last distance (see the help file page of the function
\texttt{mgedist} in \texttt{fitdistrplus} reference manual for details).
Below is an example of fit of a uniform distribution to the same dataset by maximizing the 
Kolmogorov-Smirnov distance.
<<>>=
fitdist(u,"unif",method="mge",gof="KS")
@
